---
title: "BayesCoin_Part2"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{BayesCoin_Part2}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(MATH4793Chihyu)
```
# Introduction
This is Bayes Coin Part2!

Here to visit my github: <https://github.com/chihyu702/MATH4793_CHUpackage>

# Task 1 

"bayesPosterior" is a function in the package. Given the Binomial experiment with n trials and y successes, with prior in Beta(alpha, beta). This function will produce a plot that has all three densities on the one axes, p(theta), f(y|theta), and p(theta|y). Moreover, it prints a named list containing Bayesian point and interval estimates (intervals made for a given tail area of a). 

```{r fig.width=6, fig.height=4}
bayesPosterior (n = 10, y = 4, alpha = 1, beta = 1, a = 0.025)
```

# Task 2
"bayesMixture" is a function in the package. Given the Binomial experiment with n trials and y successes mixture prior in Beta(alpha1, beta1) with p and Beta(alpha2, beta2).

This function will produce two plots, one is the mixture prior density, and another is posterior density. Moreover, it prints a named list containing Bayesian point and interval estimates of theta for a given tail area of a

```{r fig.width=6, fig.height=4}
bayesMixture(n=20, y=12, p=0.3, alpha1=2, beta1=3, alpha2=4, beta2=5, a=0.025)
```



