---
title: "Lab1"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Lab1}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
link-citations: TRUE
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(MATH4793Chihyu)
```

# Introduction

This is Lab 1!!

Here to visit my github: <https://github.com/chihyu702/MATH4793_CHUpackage>

Here is the tips to make make package: [Package making](https://canvas.ou.edu/courses/314813/pages/package-making?wrap=1)

# Latex Formula 

## Sample mean:

$$
\bar{x}_k = \frac{1}{n} \sum_{j=1}^{n} x_{jk} \quad k = 1, 2, \ldots,p
$$

it computes sample means from the n measurements

## Sample covariance:

$$
s_{ik}= \frac{1}{n} \sum_{j=1}^{n} (x_{ji} - \bar{x}_i)(x_{jk} - \bar{x}_k) \quad i = 1,2, \ldots, p, \quad k = 1,2, \ldots, p
$$

it measures the association between the ith and kth variables.

Note: $s_{ik}=s_{ki}$ for all i and k

## Sample correlation:

$$
r_{ik} = \frac{s_{ik}}{\sqrt{s_{ii}} \cdot \sqrt{s_{kk}}} = \frac{\sum_{j=1}^{n} (x_{ji} - \bar{x}_i)(x_{jk} - \bar{x}_k)}{\sqrt{\sum_{j=1}^{n} (x_{ji} - \bar{x}_i)^2} \sqrt{\sum_{j=1}^{n} (x_{jk} - \bar{x}_k)^2}}
$$

$$
i = 1,2, \ldots, p, \quad k = 1,2, \ldots, p
$$

Note: $s_{ik}=s_{ki}$ for all i and k

## Sample mean vector and covariance matrix:

$$
\bar{x} = \frac{1}{n} X^\top \mathbf{1}
$$

$$
S = \frac{1}{n-1} X^\top \left( I - \frac{1}{n} {11}^\top \right) X
$$

$$
S = \begin{bmatrix} s_{11} & s_{12} & \cdots & s_{1p} \\
\vdots & \vdots & \ddots & \vdots \\
s_{p1} & s_{p2} & \cdots & s_{pp}
\end{bmatrix}
$$

$$
D^{-1/2} = \begin{pmatrix}\frac{1}{\sqrt{s_{11}}} & 0 & \cdots & 0 \\0 & \frac{1}{\sqrt{s_{22}}} & \cdots & 0 \\\vdots & \vdots & \ddots & \vdots \\0 & 0 & \cdots & \frac{1}{\sqrt{s_{pp}}}\end{pmatrix}
$$


$$
R = \begin{bmatrix}
\frac{s_{11}}{\sqrt{s_{11}s_{11}}} & \frac{s_{12}}{\sqrt{s_{11}s_{22}}} & \cdots & \frac{s_{1p}}{\sqrt{s_{11}s_{pp}}} \\
\vdots & \vdots & \ddots & \vdots \\
\frac{s_{p1}}{\sqrt{s_{pp}s_{11}}} & \frac{s_{p2}}{\sqrt{s_{pp}s_{22}}} & \cdots & \frac{s_{pp}}{\sqrt{s_{pp}s_{pp}}}
\end{bmatrix}
= \begin{bmatrix}
1 & r_{12} & \cdots & r_{1p} \\
\vdots & \vdots & \ddots & \vdots \\
r_{p1} & r_{p2} & \cdots & 1
\end{bmatrix}
$$



Then,

$$
R = D ^{-1/2}SD^{-1/2}
$$
, where $R$ is a $p \times p$ sample correlation matrix and $D^{1/2}$ is a $p \times p$ sample standard deviation matrix



# Example of my function

## Sample mean

```{r}
vectorMean(T1_2)
```

## Sample (biased) covariance matrix

```{r}
covMatrix(T1_2)
```

## Sample correlation matrix

```{r}
corMatrix(T1_2)
```

# Assessment for the course

```{r}
data.frame(
  'Assignment group' = c('In-class quiz', 'Assignment', 'Lab', 'Exam 1', 'Exam 2', 'Project', 'Final Exam'), 
  'weight in percentage' = c('5', '20', '15', '10', '10', '10', '30')
)
```
